---
title: "Principal Componenat Analysis of 10k histograms"
author: "Romain Valabregue & Vincent Perlbarg & Vincent Guillemot & Arthur Tenenhaus"
date: "16/04/2015"
output: pdf_document
header-includes: \usepackage{graphicx}
---

This short analysis shows an Principal Component Analysis on histograms.

```{r preambule, echo=FALSE, message=FALSE}
require(signal) #for function interp1 in histo normalisation
```

# The data-set

There are 4 variables in the histogram data-set:

 * `histoMatY`: dim $n \times 512$ each line is the amplitude of the histogram (density);
 * `histoMatX`: dim $n \times 512$ each line is the $x$ axis of the histogram (range of value in each volume);
 * `meanSignal`: a normalisation factor for each sujbect (the mean value of gray and white voxel in the brain);
 * `fa`: a string that gives the path of each subject data .

```{r read_histo, echo=FALSE}
load(file.path("~","10kbrains","histo_matrix.Rdata"))
```


```{r normhisto, echo=FALSE}
new_X <- seq(0.5,150,0.5)
new_Y <-  matrix(NA, nrow=nrow(histoMatX), ncol=length(new_X))
#y2= matrix(,nrow=nrow(histoMatX),ncol=length(xx))

for (k in seq(1,nrow(histoMatX)) ) {
  y=histoMatY[k,]
  x=histoMatX[k,]
  #scale x for intensity  with mean gray/white intensity
  x2 = x/meanSignal[k]*100  
  #interpolate to have the same x sample
  y2 = interp1(x2,y,new_X)    
  #the extremite of the histogram (max of x) varie, so put zero if not defined
  y2[is.na(y2)]=0    
  new_Y[k,] = y2    
}
```

# Principal Component Analysis


Figure \ref{fig:plotpca} shows the first two components of a PCA applied to the normalized histograms.

```{r pca, echo=FALSE}
Hy <- new_Y
rpca <- princomp(Hy, cor=TRUE)
```

```{r plotpca, echo=FALSE, fig.cap="The first two components.", fig.align="center"}
plot(rpca$scores[,1], rpca$scores[,2], pch=16, 
     xlab="First Component", ylab="Second Component")
```

